---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# truelies

 [![CRAN status](https://www.r-pkg.org/badges/version/truelies)](https://cran.r-project.org/package=truelies)
[![Travis build status](https://travis-ci.org/hughjonesd/truelies.svg?branch=master)](https://travis-ci.org/hughjonesd/truelies)
[![AppVeyor build status](https://ci.appveyor.com/api/projects/status/github/hughjonesd/truelies?branch=master&svg=true)](https://ci.appveyor.com/project/hughjonesd/truelies)

`truelies` implements Bayesian methods, described in 
[Hugh-Jones (2019)](https://link.springer.com/article/10.1007/s40881-019-00069-x), 
for estimating the proportion of liars in coinflip-style experiments, where
subjects report a random outcome and are paid for reporting a "good" outcome.

For R source for the original paper, see https://github.com/hughjonesd/GSV-comment.

## Installation

``` r
# stable version on CRAN
install.packages("truelies")

# latest version from github
remotes::install_github("hughjonesd/truelies")
```

## Example

If you have 33 out of 50 reports of heads in a coin flip experiment:

```{r example}
library(truelies)
d1 <- update_prior(heads = 33, N = 50, P = 0.5, prior = dunif)
plot(d1)

dist_mean(d1)

# 95% confidence interval, using hdrcde
dist_hdr(d1, 0.95)
```

## Citation

`r format(citation("truelies"), style = "text")`

## Bibtex 

```{r, echo = FALSE, comment = NA}
cit <- citation("truelies")
cit$key <- "hughjones2019"
print(cit, style = "Bibtex")
```
